NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2017-12-08 Manuscript/manuscriptPS.tex
Update table with simulated systems

    POPC:POPS (5:1)/Na$^+$  & CHARMM36 \cite{klauda10,??} \todoi{Correct citation for CHARMM POPS}        &0 & 0        & ? 			   		& ? & 0  & ?  & ? & ? & \cite{??}
    \todoi{Details to be filled and data to be uploaded in Zenodo by Ollila.}  \\
    POPG/Na$^+$  & CHARMM36 \cite{??} \todoi{Correct citation for CHARMM POPG}        &0 & 0        & ? 			   		& ? & 0  & ?  & ? & ? & \cite{??}
    \todoi{Details to be filled and data to be uploaded in Zenodo by Ollila.}  \\
    POPG/Na$^+$  & Slipids \cite{jambeck13}     &0 & 0        & 288 			   		& 10664 & 0  & 298  & 250 & 100 & \cite{slipidsPOPGfiles} \\
    DPPG/Na$^+$  & Slipids \cite{jambeck13}     &0 & 0        & 288 			   		& 11232 & 0  & 314  & 200 & 100 & \cite{slipidsDPPGfiles} \\
    DPPG/Na$^+$  & Slipids \cite{jambeck13}     &0 & 0        & 288 			   		& 11232 & 0  & 298  & 400 & 100 & \cite{slipidsDPPGfilesT298K} \\

>>>>

    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,??} \todoi{Correct citation for CHARMM POPS}        &0 & 0        & 110:22	   		& 4935 & 0  & 298  & 100 & 100 \todoi{Equilibration?} & \cite{charmm36pops+83popcT298K}  \\
%    \hline
%    POPG/Na$^+$  & CHARMM36 \cite{??} \todoi{Correct citation for CHARMM POPG}        &0 & 0        & ? 			   		& ? & 0  & ?  & ? & ? & \cite{??}
%    \todoi{Details to be filled and data to be uploaded in Zenodo by Ollila.}  \\
%    POPG/Na$^+$  & Slipids \cite{jambeck13}     &0 & 0        & 288 			   		& 10664 & 0  & 298  & 250 & 100 & \cite{slipidsPOPGfiles} \\
%    \hline
%    DPPG/Na$^+$  & Slipids \cite{jambeck13}     &0 & 0        & 288 			   		& 11232 & 0  & 314  & 200 & 100 & \cite{slipidsDPPGfiles} \\
%    DPPG/Na$^+$  & Slipids \cite{jambeck13}     &0 & 0        & 288 			   		& 11232 & 0  & 298  & 400 & 100 & \cite{slipidsDPPGfilesT298K} \\
